---
title: "Visual Angle in R"
---

Here are some simple R functions I've found useful for calculating [visual angle](https://en.wikipedia.org/wiki/Visual_angle) or inferring size from reports of visual angle in papers.

The function ``visAngle()`` takes two arguments; the size of the stimulus and the viewing distance of the observer (both in the same units). It returns the visual angle of the stimulus.

```{r}
visAngle <- function(size, distance){
  # this function calculates visual angle
  # size and distance must be in the same units
  Rad = 2*atan(size/(2*distance))
  Ang = Rad*(180/pi)
  return(Ang)
}

visAngle(size = 1, distance = 57) # why people use 57 cm as viewing distance

```

Occasionally, to replicate a paradigm, you'll want to calculate the size of a stimulus from a reported visual angle and viewing distance. The function ``desiredSize()`` takes a visual angle and distance and returns the stimulus size in the same units as the distance.

```{r}
desiredSize <- function(visAngle, distance){
  # this function gives desired size of stimulus
  # given visual angle and distance
  # size returned is in same units and distance
  Rad = visAngle/(180/pi) # or pi*(visAngle/180)
  size = 2*distance*tan(Rad/2)
  return(size)
}

desiredSize(visAngle = 2.5, distance = 40)
```

Proof they actually work!

```{r}
dist = 50
size = 5
ang = visAngle(size = size, distance = dist)

desiredSize(visAngle = ang, distance = dist)
```

