---
name: Stephen Rhodes
position: "Clinical Research Biostatistician III"
address: "University Hospitals Cleveland Medical Center"
www: stephenrho.github.io
email: "stephen.rhodes@uhhospitals.org"
github: stephenrho
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 414141
urlcolor: blue
linkcolor: blue
docname:  Resume
output: 
  vitae::hyndman
header-includes:
  - \pagenumbering{gobble}
---

<!-- googlescholar: VXD5emcAAAAJ&hl -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae); library(tibble)
```

# Skills and Expertise

- **R + R-Studio**: for analysis, report building, package and shiny app development; used for over 10 years
- **Other Programming Languages**: SLURM (for high performance computing); SQL (for databases); Stan (for Bayesian modeling); python (for predictive modeling)
- **Clinical Research**: clinical trial design; analysis of large healthcare databases; causal inference with observational data; Epic Cosmos superuser
- **Communication**: both written and spoken to both expert and lay audiences

# Experience

```{r}
exp = tribble(
  ~ role, ~ years, ~ instit, ~ city, ~ details,
  # UH
  "Clinical Research Biostatistician III", "2022-present", "University Hospitals, Cleveland Medical Center", "Cleveland OH, USA", 
  c("Primary statistician on \\href{https://www.pcori.org/research-results/2024/bulking-versus-sling-treating-stress-urinary-incontinence-time-vaginal-prolapse-repair}{multi-center randomized trial funded by PCORI.}",
    "Extract information from large admininstrative/claims databases (Premier Healthcare Database, Marketscan, ICES (Ontario), Epic Cosmos).", 
    "Develop and evaluate clinical prediction models. Wrote two R packages that implement best-practices for internal validation (\\href{https://cran.r-project.org/package=pminternal}{pminternal}) and assessing calibration (\\href{https://cran.r-project.org/package=pmcalibration}{pmcalibration}) of prediction models.",
    "Provide seminars on concepts and approaches in biostatistics to residents, fellows, and research staff."),
  # RRI
  "Postdoctoral Fellow", "2019-2021", "Baycrest Hospital, Rotman Research Institute (University of Toronto)", "Toronto ON, CA", 
  c("Devised and conducted experiments on age-related changes to short- and long-term memory.",
    # "Developed a project using functional magnetic resonance imaging to decode currently active neural representations in short-term memory (shelved due to Covid-19).",
    "Used neural network image classification models to measure image similarity for testing against human perception and memory.",
    "Developed and led a workshop on Bayesian data analysis \\href{https://github.com/stephenrho/bayes-workshop}{(materials here)}."),
  # miz
  "Postdoctoral Fellow", "2016-2019", "University of Missouri, Dept. of Psychological Sciences", "Columbia MO, USA", 
  c("Part of a collaboration on aging and memory between groups in the US, UK, and Switzerland (\\url{http://womaac.psy.ed.ac.uk/}).",
    "Led the development of analysis pipelines (\\href{https://osf.io/72j4m/}{example here}) and performed analyses of experimental data using generalized linear mixed effects models.",
    "Developed a protocol for data documentation and archiving to ensure reproducibility.",
    "Led two meta-analysis projects synthesizing findings in the literature on memory and aging.",
     # Used meta-analytic models to provide new insights into long-standing research questions. Published in \\href{https://psycnet.apa.org/fulltext/2019-24512-001.html}{Psychology \\& Aging} and \\href{https://link.springer.com/article/10.3758/s13423-019-01649-y}{Psychonomic Bulletin \\& Review}.
    "Co-developed and led a two day workshop on the statistical modeling using maximum likelihood and Bayesian estimation techniques \\href{https://github.com/stephenrho/CognitiveModelingWorkshop}{(materials here)}.")
)

exp %>%
  detailed_entries(what = instit, when = years, with = role, where = city, why = details, .protect = F)
```

# Education

```{r}

tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  #"Postdoctoral Fellow", "2019-2021", "Rotman Research Institute", "Toronto ON, CA",
  #"Postdoctoral Fellow", "2016-2019", "University of Missouri", "Columbia MO, USA",
  "PhD Cognitive Psychology", "2012-2016", "The University of Edinburgh", "Edinburgh, UK",
  "MSc Human Cognitive Neuropsychology", "2011-2012", "The University of Edinburgh", "Edinburgh, UK",
  "BSc (hons) Psychology", "2008-2011", "University of Leeds", "Leeds, UK"
) %>% 
  detailed_entries(what = Degree, when = Year, with = Institution, where = Where)
```
