---
name: Stephen Rhodes
position: "Clinical Research Biostatistician III"
address: "University Hospitals Cleveland Medical Center"
# www: stephenrho.github.io
email: "stephen.rhodes@uhhospitals.org"
github: stephenrho
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 414141
output: 
  vitae::awesomecv
---

<!-- googlescholar: VXD5emcAAAAJ&hl -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae); library(tibble)
```

# Skills and Expertise

- **R** - used for working with data and analysis for 10+ years. Developed package `pmcalibrate`
- **python** - Intermediate proficiency
- **stan** - for Bayesian modeling
- **SQL** - used for 2 years
- **Clinical Prediction Modeling** - developing and evaluating diagnostic and prognostic models, following well established guidelines (e.g., TRIPOD)
- **Large Healthcare Databases** - worked with several large databases from different sources (claims/EHR, insurance, state wide cancer registry)

\begin{cvskills}
	
	\cvskill
	{ R \& R-Studio }
	{ regularly used packages: brms, lme4, ggplot2, plotly, plyr, knitr, Shiny, rmarkdown }
	
	\cvskill	
	{ Python }
	{ regularly used packages: numpy, pandas, scipy, psychopy, sklearn}
	
	\cvskill
	{ Other Languages }
	{ SLURM; SQL; Matlab/ octave (occasional use)}
	
	\cvskill
	{ Bayesian Modeling }
	{ using the Just Another Gibbs Sampler (JAGS) and Stan programming languages}
	
	\cvskill
	{ Communication }
	{ to both technical and non-technical audiences }
	
	%---------------------------------------------------------
	%\cvskill
	%{R \& R-Studio}
	%{highly proficient (over 7 years). Regularly used packages: brms, lme4, ggplot2, plotly, plyr}
	
	%---------------------------------------------------------
	%\cvskill
	%{Python} 
	%{highly proficient (over 5 years). Regularly used packages: numpy, pandas, scipy, psychopy} 
	
	%---------------------------------------------------------
	%\cvskill
	%{Bayesian Modeling} 
	%{with JAGS and Stan - proficient (over 3 years)} 
	
	%---------------------------------------------------------
	%\cvskill
	%{Matlab/ octave} 
	%{beginner (1 year)} 
	
	%---------------------------------------------------------
	%\cvskill
	%{SQL} 
	%{beginner (3 months)} 
	
	%---------------------------------------------------------
\end{cvskills}


# Experience

```{r}
exp = tribble(
  ~ role, ~ years, ~ instit, ~ city, ~ details,
  "Clinical Research Biostatistician III", "2021-present", "University Hospitals, Urology Institute", "Cleveland OH, USA", c("Worked with many large scale healthcare databases (premier, OCISS, marketscan, trinetx, allofus)", "Developed clinical prediction models", "Causal inference \\href{test}{www.test.com}"),
  
  "Postdoctoral Fellow", "2019-2021", "Baycrest Hospital, Rotman Research Institute (University of Toronto)", "Toronto ON, CA", c(),
  
  "Postdoctoral Fellow", "2016-2019", "University of Missouri, Dept. of Psychological Sciences", "Columbia MO, USA", c(),
  
)

exp %>%
  detailed_entries(what = instit, when = years, with = role, where = city, why = details, .protect = F)
```


# Education

```{r}

tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  #"Postdoctoral Fellow", "2019-2021", "Rotman Research Institute", "Toronto ON, CA",
  #"Postdoctoral Fellow", "2016-2019", "University of Missouri", "Columbia MO, USA",
  "PhD Cognitive Psychology", "2012-2016", "The University of Edinburgh", "Edinburgh, UK",
  "MSc Human Cognitive Neuropsychology", "2011-2012", "The University of Edinburgh", "Edinburgh, UK",
  "BSc (hons) Psychology", "2008-2011", "University of Leeds", "Leeds, UK"
) %>% 
  detailed_entries(what = Degree, when = Year, with = Institution, where = Where)
```
